
## Group Number: 7
## Group Members: Soma Dipti, Prashant Mittal, Raj Bhanvadia, Somnath Bhattacharjee, Allhad Abhyankar
## Title: Analyzing the Airbnb listings in Toronto and Vancouver
## Data 606 Final Project

```{r}

#Required libraries
library(tidyr)
library(survey) 
library(sampling)
library('ISLR')
library('ggplot2') 
library(MASS)
library(tree) 
library(dplyr)
library(ggcorrplot) 
library(gridExtra)
library(stringr)
library(ggplot2)
library(car)
library(cowplot)
library(klaR)
library(MASS)
library(rpart)
library(rpart.plot)
library(caret)
library(pROC)
```

```{r}
#Pre-Processing of Data

airbnb = read.csv("Toronto_Airbnb_Data.csv") # reading data file

names(airbnb) #names of attributes
dim(airbnb) #dimensions
summary(airbnb) #statistical details of attributes

airbnb=na.omit(airbnb) #removing/ignoring null values
```

# Data Pre-processing :
# For Analysis - Location Considered c("Toronto, Canada","Vancouver, Canada"):
```{r}
airbnb.data=filter(airbnb,airbnb$host_location %in% c("Toronto, Canada","Vancouver, Canada")) 
airbnb.data = airbnb.data %>% mutate(
room_type = if_else(room_type == "Entire home/apt", "ENTIRE", if_else (room_type=="Private room" , "PRIVATE" ,"SHARED")),
property_type = if_else(str_detect(property_type, "Entire"), "ENTIRE", if_else (str_detect(property_type, "Private") , "PRIVATE" ,if_else(str_detect(property_type, "Shared"),"SHARED","MISC")))
                        )%>% dplyr::select(room_type, property_type, host_location, host_response_rate, host_is_superhost, host_listings_count, price,minimum_nights, maximum_nights,number_of_reviews)

airbnb.data$host_response_rate=replace(airbnb.data$host_response_rate, airbnb.data$host_response_rate=='N/A', NA)
airbnb.data$host_is_superhost=replace(airbnb.data$host_is_superhost, airbnb.data$host_is_superhost=='', "False")

airbnb.data$host_response_rate=gsub('%','',airbnb.data$host_response_rate)

airbnb.data$host_response_rate = as.numeric((airbnb.data$host_response_rate))
head(airbnb.data) #top rows
dim(airbnb.data) #dimensions of data



```

```{r}
airbnb.data['price'] <- gsub( ",", "", as.character(airbnb.data$price) )
airbnb.data['price'] <- as.numeric(gsub( "\\$", "", as.character(airbnb.data$price) ,ignore.case=T))
airbnb.data <- filter( airbnb.data, price <= 1000)

head(airbnb.data,5)

dim(airbnb.data)
```

# Converting Categorical Data to Factor:
```{r}
airbnb.data$host_location=as.factor(airbnb.data$host_location)
airbnb.data$room_type=as.factor(airbnb.data$room_type)
airbnb.data$property_type=as.factor(airbnb.data$property_type)
airbnb.data$host_is_superhost=as.factor(airbnb.data$host_is_superhost)
head(airbnb.data,5)
```


# Exploratory Data Analysis:

```{r}
ggplot(airbnb.data, aes(x=host_is_superhost, fill=host_is_superhost)) + geom_bar() + xlab("Super host") + ylab("Count") + ggtitle("Host Designated as SuperHost ") + scale_fill_discrete(name = "Super Host") + theme(plot.title = element_text(hjust = 0.5))
```

```{r}

ggplot(data = airbnb.data, aes(x = host_is_superhost, y=price, color = host_is_superhost)) + geom_boxplot( na.rm=TRUE,show.legend = FALSE)+ xlab("Type of Host") + ylab('Price')+ ggtitle("Price for Airbnb Host Type") + theme(plot.title = element_text(hjust = 0.5))



```
```{r}
ggplot(data = airbnb.data, aes(x = host_is_superhost, y=host_listings_count, color = host_is_superhost)) + geom_boxplot( na.rm=TRUE,show.legend = FALSE)+ xlab("Type of Host") + ylab('Listing Count')+ ggtitle("Listing Count for Airbnb Host Type") + theme(plot.title = element_text(hjust = 0.5))

```


```{r}
m=mean(airbnb.data$price)
ggplot(data = airbnb.data, aes(x =price)) + geom_histogram( binwidth=10, na.rm=TRUE, fill="steelblue") + theme_minimal() + xlab('Price')+ ylab('Count')+ ggtitle("Histogram of Airbnb Price Distribution")+ theme(plot.title = element_text(color="black", size=14))+geom_vline(xintercept = m, col="orange") + theme(plot.title = element_text(hjust = 0.5))
```
```{r}
ggplot(data = airbnb.data, aes(x = host_is_superhost, y=minimum_nights, color = host_is_superhost)) + geom_boxplot( na.rm=TRUE, show.legend = FALSE)+ xlab("Host is Superhost") + ylab('Minimum Nights')+ ggtitle("Minimum Nights for Host Type")+ coord_flip() + theme(plot.title = element_text( size=14), legend.title = element_blank())+ theme(plot.title = element_text(hjust = 0.5))


ggplot(data = airbnb.data, aes(x = host_is_superhost, y=maximum_nights, color = host_is_superhost)) + geom_boxplot( na.rm=TRUE, show.legend = FALSE)+ xlab("Host is Superhost") + ylab('Maximum Nights')+ ggtitle("Maximum Nights for Host Type")+ coord_flip() + theme(plot.title = element_text( size=14), legend.title = element_blank()) + theme(plot.title = element_text(hjust = 0.5))

```


# Analysis Part 1: Logistic Regression:

```{r}
dim(airbnb.data)
table(airbnb.data$host_is_superhost)
str(airbnb.data)


```

```{r}
#logistic
#For stratified sampling, a 30 % sample was taken from the main dataset
airbnb.data$host_is_superhost = if_else(airbnb.data$host_is_superhost=="False",0,1)

n=0.30 * dim(airbnb.data)[1]
popsize <- table(airbnb.data$host_is_superhost)
popsize
propalloc <- (n*popsize/sum(popsize))
propalloc
unique(airbnb.data$host_is_superhost)
```

# Taking Sampling using Strata Sampling and divide data into train and test:

```{r}
set.seed(10)
idx = sampling:::strata(airbnb.data, stratanames=c("host_is_superhost"), size=c(2585, 940), method="srswor")
airbnb_train =airbnb.data[idx$ID_unit, ]
airbnb_test = airbnb.data[-idx$ID_unit, ]

dim(airbnb_train)
table(airbnb_train$host_is_superhost)



```
```{r}
#"Checking for Variance Inflation Factor (vif)" for each coefficient**
names(airbnb_train)
```

# Checking Multicollinearity:
```{r}
# Logistic regression model construction

model.fit = glm(host_is_superhost ~ factor(room_type)+ factor(host_location) + host_response_rate + host_listings_count
                 +price + minimum_nights + maximum_nights +number_of_reviews, family = binomial, data=airbnb_train)

vif(model.fit)

summary(model.fit)
#Since vif is close to 1, No multicollinearity detected.

```

# Model using significant paramters:

```{r}
#keeping significant terms in model

model1.fit = glm(host_is_superhost ~  host_response_rate + host_listings_count+ maximum_nights+number_of_reviews, family = binomial, data=airbnb_train)
summary(model1.fit)
```

# Prediction using test data and calculate miscalculation rate:
```{r}
prob.predict = predict(model1.fit, airbnb_test, type='response')
Predict = rep(0, dim(airbnb_test)[1])
Predict[prob.predict>=0.5]=1
Actual = airbnb_test$host_is_superhost
cf=table(Predict, Actual)

cf

mis_class_Error=((cf[2,1]+cf[1,2])/nrow(airbnb_test))
mis_class_Error

```
# Linear Discriminant Analysis:
# Testing Normality:

```{r}
superhost.yes <- subset(airbnb.data, host_is_superhost == "1")
#superhost.yes
superhost.no = subset(airbnb.data, host_is_superhost == "0")
#superhost.no
variable_1 <- c("host_listings_count","host_response_rate","maximum_nights","number_of_reviews")
par(mfrow = c(1, 4))
for(i in variable_1) {
qqnorm(superhost.yes[[i]]); qqline(superhost.yes[[i]], col = 4)}

par(mfrow = c(1, 4))
for(i in variable_1) {
qqnorm(superhost.no[[i]]); qqline(superhost.no[[i]], col = 4)}

```

```{r}
#To check for data is normalized or not

shapiro.test(superhost.yes$maximum_nights)
shapiro.test(superhost.yes$host_response_rate)
shapiro.test(superhost.yes$host_listings_count)
shapiro.test(superhost.yes$number_of_reviews)
#data is not normal , we will still keep the paramters
```



# Linear Discriminant Analysis using all variables:

```{r warning=FALSE}

options(warn = -1)
lda.fit = lda(host_is_superhost ~room_type+ host_location + host_response_rate + host_listings_count+price + minimum_nights + maximum_nights+number_of_reviews, data=airbnb_train)

#host_response_rate + host_listings_count+ maximum_nights
lda.fit
lda.pred=predict(lda.fit, airbnb_test)
```

# Prediction and calculate miscalculation error:
```{r}
cf.lda=table(lda.pred$class, airbnb_test$host_is_superhost)
cf.lda
misCalcError.lda=((cf.lda[2,1]+cf.lda[1,2])/nrow(airbnb_test))
misCalcError.lda
```


# Residual plot of model:

```{r}
qplot(residuals(model.fit),
      geom="histogram",
      binwidth = 0.1,  
      main = "Histogram of Residuals", 
      xlab = "residuals", 
      fill=I("blue")) + theme(plot.title = element_text(hjust = 0.5))
```

# Stacked Histogram for Discriminant Function values:
```{r}

ldahist(data = lda.pred$x[,1], g = airbnb_test$host_is_superhost)


```




# Performing QDA and Predicting:

```{r warning = FALSE}

qda.fit =qda(host_is_superhost ~factor(room_type)+ factor(host_location) + host_response_rate + host_listings_count+price + minimum_nights + maximum_nights+ number_of_reviews, data=airbnb_train)

qda.fit


qda.pred=predict(qda.fit, airbnb_test)
```

# Confusion Matrix and Miscalculation error for QDA:
```{r}
cf.qda=table(qda.pred$class, airbnb_test$host_is_superhost)

cf

misCalcError.qda=((cf.qda[2,1]+cf.qda[1,2])/nrow(airbnb_test))
misCalcError.qda
```

# Part 2: Classification Method using Decision Tree:
```{r}

airbnb.rf <- na.omit(airbnb.data)
dim(airbnb.rf)
head(airbnb.rf,4)
```

# Create train and test data:
```{r}

create_train_test <- function(data, size = 0.8, train = TRUE) {

    n_row = dim(data)[1]
    total_row = size * n_row
    train_sample=rep(0,total_row)
    train_sample = 1: total_row
    if (train == TRUE) {
        return (data[train_sample, ])
    } else {
        return (data[-train_sample, ])
    }
}
```

# Calculate Probability:
```{r}

data_train <- create_train_test(airbnb.rf, 0.8, train = TRUE)
data_test <- create_train_test(airbnb.rf, 0.8, train = FALSE)
#dim(data_train)
#dim(data_test)
prop.table(table(data_train$host_is_superhost))


```

# Plot Decision Tree Model:
```{r}

fit <- rpart(host_is_superhost~., data = data_train, method = 'class')
rpart.plot(fit, extra = 106)
```


# Feature Importance:
```{r}
fit$variable.importance
```

# Prediction, confusion matrix and getting accuracy:
```{r}
predict_unseen <-predict(fit, data_test, type = 'class')
table_mat <- table(data_test$host_is_superhost, predict_unseen)
table_mat

accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
print(paste('Accuracy for Test', accuracy_Test))
```
```{r}
tree.superhost=tree(factor(host_is_superhost)~.,airbnb.data, subset= unlist(data_train))
cv.tree.superhost=cv.tree(tree.superhost, FUN=prune.misclass)
plot(cv.tree.superhost$size,cv.tree.superhost$dev, type="b")

cat("From the plot, we decide not to prune, as Accuracy is decreasing")
```

# Tune the hyper-parameters:
```{r}
accuracy_tune <- function(fit) {
    predict_unseen <- predict(fit, data_test, type = 'class')
    table_mat <- table(data_test$host_is_superhost, predict_unseen)
    accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
    accuracy_Test
}
```

```{r}
control <- rpart.control(minsplit = 4,
    minbucket = round(5 / 3),
    maxdepth = 3,
    cp = 0)
tune_fit <- rpart(host_is_superhost~., data = data_train, method = 'class', control = control)
accuracy_tune(tune_fit)
```


# K fold validation for lda and decision tree:
```{r warning=FALSE}
folds<-createFolds(airbnb.rf$host_is_superhost, k=10)
fold1<-airbnb.rf[folds$Fold1,]
table(fold1$host_is_superhost)

misclassification.lda<-function(idx){
train<-airbnb.rf[-idx,]
test<-airbnb.rf[idx,]
fit<-lda(host_is_superhost~., data=train)
pred<-predict(fit,test,type = "class")
return(1-mean(pred$class==test$host_is_superhost))
}

mis_rate.lda=lapply(folds,misclassification.lda)

m.lda=mean(as.numeric(mis_rate.lda))
cat("\n","Miscalculation rate from k fold validation performed for lda",m.lda)

misclassification.decisionTree<-function(idx){
train<-airbnb.rf[-idx,]
test<-airbnb.rf[idx,]
fit2 <- rpart(host_is_superhost~., data = data_train, method = 'class')
pred2<-predict (fit2, test,type = "class")
return(1-mean(pred2==test$host_is_superhost))
}

mis_rate.lda=lapply(folds,misclassification.decisionTree)
m.dt=mean(as.numeric(mis_rate.lda))
cat("\n","Miscalculation rate from K fold validation performed for decision tree",m.dt)
```

# Plotting k fold accuracy for decision tree:
```{r}
pred.decisionTree<-function(idx){
train<-airbnb.rf[-idx,]
test<-airbnb.rf[idx,]
fit2 <- rpart(host_is_superhost~., data = data_train, method = 'class')
pred2<-predict (fit2, test,type = "class")
check=ifelse(pred2==test$host_is_superhost,1,0)
df=c(check)

return (mean(df))
}

p=lapply(folds,pred.decisionTree)
p1=data.frame(p)
df_t <- t(p1)
col=data.frame(colnames(p1))
df=data.frame("fold"=col,"accuracy"=df_t)
colnames(df)=c("Folds","Accuracy")


ggplot(data=df, aes(x=Folds, y=Accuracy, group= 1)) +
geom_boxplot(color="maroon") +
geom_point() + 
ggtitle("Accuracy Distribution from K Folds") + 
theme(plot.title = element_text(hjust = 0.5))


```

# Naive Bayes Algorithm:
```{r}

set.seed(100)
trctrl <- trainControl(method = "cv", number = 10, savePredictions=TRUE)
nb_fit <- train(factor(host_is_superhost) ~., data = airbnb.rf, method = "naive_bayes", trControl=trctrl, tuneLength = 0)
nb_fit
```

```{r}
pred <- nb_fit$pred
pred$equal <- ifelse(pred$pred == pred$obs, 1,0)

eachfold <- pred %>%                                        
  group_by(Resample) %>%                         
  summarise_at(vars(equal),                     
               list(Accuracy = mean))              


ggplot(data=eachfold, aes(x=Resample, y=Accuracy, group=1)) +
geom_boxplot(color="maroon") +
geom_point() +
theme_minimal()+ ggtitle("Box-Plot: Accuracy vs Resampling for K-10 folds") +theme(plot.title = element_text(hjust = 0.5))
```



# Apply the Pearson's Chi-square test to the table with variable "maxNight_level" and response variable "super host", check its p-value:


```{r}
#Hypothesis Statement:
#ho: maxNight_level and host_is_superhost are independent
#ha: maxNight_level and host_is_superhost are related

a1<-airbnb.data[order(airbnb.data$maximum_nights),]
# We group the patients as per their maximum nights (<100, 101-500, >500)
L1=sum(as.numeric(airbnb.data$maximum_nights<=100))
L2=sum(as.numeric(airbnb.data$maximum_nights<=500))-L1
L3=dim(airbnb.data)[1]-L1-L2

cat(L1,L2,L3)
maxNight_level<-c(rep ('1-100', L1), rep ('101-500', L2), rep ('500 above', L3))
a1<-cbind(a1, maxNight_level)
maxNight_level_SH<-table(a1$maxNight_level, a1$host_is_superhost )
maxNight_level_SH
chisq.test(maxNight_level_SH)

#We reject Ho stating maxNight_level and host_is_superhost are independent and accepts the ha.
```

```{r}
a1<-airbnb.data[order(airbnb.data$maximum_nights),]
# We group the patients as per their maximum number_of_reviews (<10, 11-50, >50)
L1=sum(as.numeric(a1$number_of_reviews <=10))
L2=sum(as.numeric(a1$number_of_reviews<=50))-L1
L3=dim(a1)[1]-L1-L2


reviews_level<-c(rep ('1=0-10', L1), rep ('11-50', L2), rep ('50 above', L3))
a1<-cbind(a1, reviews_level)
reviews_level_SH<-table(a1$reviews_level, a1$host_is_superhost )
reviews_level_SH
chisq.test(reviews_level_SH)

#We reject Ho stating reviews_level and host_is_superhost are independent and accepts ha.
```


```{r}
a1<-airbnb.data[order(airbnb.data$host_listings_count),]
# We group the patients as per their maximum host listing (<=3, 4-10, >10)
L1=sum(as.numeric(a1$host_listings_count <=3))
L2=sum(as.numeric(a1$host_listings_count<=10))-L1
L3=dim(a1)[1]-L1-L2
cat(L1,L2,L3)

host_listings_level<-c(rep ('1-3', L1), rep ('4-10', L2), rep ('10 above', L3))
a1<-cbind(a1, host_listings_level)
hostListing_level_SH<-table(a1$host_listings_level, a1$host_is_superhost )
hostListing_level_SH
chisq.test(hostListing_level_SH)

#We reject Ho stating  host listing and host_is_superhost are independent and accepts ha.



```

# Classification model for host review levels:
# Distribute host levels to create categories and performed chi square test:
```{r}

a1<-airbnb.data[order(airbnb.data$host_listings_count),]
# We group the patients as per their maximum host listing (<=3, 4-10, >10)
L1=sum(as.numeric(a1$host_listings_count <=3))
L2=sum(as.numeric(a1$host_listings_count<=10))-L1
L3=dim(a1)[1]-L1-L2
cat(L1,L2,L3)

host_listings_level<-c(rep ('1-3', L1), rep ('4-10', L2), rep ('10 above', L3))
a1<-cbind(a1, host_listings_level)
hostListing_level_SH<-table(a1$host_listings_level, a1$host_is_superhost )
hostListing_level_SH
chisq.test(hostListing_level_SH)


#p-value : 0.00000000000000022 < 0.05 (alpha)

```


```{r}

m=mean(airbnb.data$number_of_reviews)
ggplot(data = airbnb.data, aes(x =number_of_reviews)) + geom_histogram( binwidth=10, na.rm=TRUE, fill="steelblue") + theme_minimal() + xlab('Number of Reviews')+ ylab('Count')+ ggtitle("Histogram of Airbnb Number of Review Distribution")+ theme(plot.title = element_text(color="black", size=14))+geom_vline(xintercept = m, col="orange") + theme(plot.title = element_text(hjust = 0.5))

summary(airbnb.data$number_of_reviews)

```

# Created tailored data set for analysis:

```{r}
# We group the patients as per their number of reviews(<=3, 4-10, >10)
L1=sum(as.numeric(a1$number_of_reviews ==0))
L2=sum(as.numeric(a1$number_of_reviews<=10))-L1
L3=sum(as.numeric(a1$number_of_reviews<=50))-L1 -L2
L4=dim(a1)[1]-L1-L2 -L3
cat(L1,L2,L3,L4)

host_review_level<-c(rep ('No review', L1), rep ('moderately less reviewd', L2), rep ('moderately reviewed', L3),rep('highly reviewed',L4))
airbnb.1=cbind(airbnb.data,host_review_level)
head(airbnb.1,10)


```



# Sampling to divide data for training and testing:

```{r}
n=0.30 * dim(airbnb.1)[1]
popsize <- table(airbnb.1$host_review_level)
popsize
propalloc <- (n*popsize/sum(popsize))
propalloc
unique(airbnb.1$host_review_level)
```


```{r}
idx = sampling:::strata(airbnb.1, stratanames=c("host_review_level"), size=c(730.8, 1254.0,919.5,621.3), method="srswor")
ratinglevel_train =airbnb.1[idx$ID_unit, ]
ratinglevel_test = airbnb.1[-idx$ID_unit, ]

dim(ratinglevel_train)
prop.table(table(ratinglevel_test$host_review_level))
```


```{r}
fit_review_levels <- rpart(factor(host_review_level)~ room_type +property_type+host_location+host_response_rate+host_is_superhost+host_is_superhost+host_listings_count+
               price+minimum_nights+maximum_nights ,data = ratinglevel_train, method = 'class',cp=0.008) #Complexity Parameter

rpart.plot(fit_review_levels) #plotting tree

summary(fit_review_levels) #summary of fit review



```

# Feature Importance:
```{r}
fit_review_levels$variable.importance
```


```{r}
summary(fit_review_levels)

```


```{r}
printcp(fit_review_levels)
plotcp(fit_review_levels)
```




```{r}
pred.tree = predict(fit_review_levels, ratinglevel_test, type = "class")
summary(pred.tree)
tb2=table(pred.tree,ratinglevel_test$host_review_level)
tb2
accuracy_Test <- sum(diag(tb2)) / sum(tb2)
print(paste('Accuracy for test', accuracy_Test))
```


```{r}


p1 <- predict(fit_review_levels, ratinglevel_test, type = 'prob')
p1 <- p1[,2]

r <- multiclass.roc(ratinglevel_test$host_review_level, p1, percent = TRUE)
roc <- r[['rocs']]
r1 <- roc[[1]]
plot.roc(r1,
         print.auc=TRUE,
         auc.polygon=TRUE,
         grid=c(0.1, 0.2),
         grid.col=c("green", "red"),
         max.auc.polygon=TRUE,
         auc.polygon.col="lightblue",
         print.thres=TRUE,
         main= 'ROC Curve')


```


```{r}
tree.review_level=tree(factor(host_is_superhost)~.,airbnb.rf, subset= unlist(ratinglevel_train))
cv.tree.reviews=cv.tree(tree.review_level, FUN=prune.misclass)
plot(cv.tree.reviews$size,cv.tree.reviews$dev, type="b")



cat("From the plot, we decide not to prune, as Accuracy is decreasing")
```


# Classification Model for Host Location:
# Resampling based for splitting data:

```{r}
n= 0.30*dim(airbnb)[1]
popsize <- table(airbnb.1$host_location)
popsize
propalloc <- (n*popsize/sum(popsize))
propalloc
unique(airbnb.1$host_location)
```


```{r}
idx = sampling:::strata(airbnb.1, stratanames=c("host_location"), size=c(25.67,5002.03), method="srswor")
hostloc_train =airbnb.1[idx$ID_unit, ]
hostloc_test = airbnb.1[-idx$ID_unit, ]

prop.table(table(hostloc_train$host_location))
```


```{r}
tree.loc <- rpart(factor(host_location)~ room_type +property_type+host_location+host_response_rate+host_is_superhost+host_is_superhost+host_listings_count+
               price+minimum_nights+maximum_nights ,data = hostloc_train, method = 'class',cp=0.008)
rpart.plot(tree.loc)

summary(tree.loc)


printcp(tree.loc)
plotcp(tree.loc)

```

```{r}
tree.loc$variable.importance

pred.tree = predict(tree.loc, hostloc_test, type = "class")
summary(pred.tree)
tb1=table(pred.tree,hostloc_test$host_location)
tb1
accuracy_Test <- sum(diag(tb1)) / sum(tb1)
print(paste('Accuracy for test', accuracy_Test))

```

```{r}


p1 <- predict(tree.loc, hostloc_test, type = 'prob')
p1 <- p1[,2]

r <- multiclass.roc(hostloc_test$host_location, p1, percent = TRUE)
roc <- r[['rocs']]
r1 <- roc[[1]]
plot.roc(r1,
         print.auc=TRUE,
         auc.polygon=TRUE,
         grid=c(0.1, 0.2),
         grid.col=c("green", "red"),
         max.auc.polygon=TRUE,
         auc.polygon.col="lightblue",
         print.thres=TRUE,
         main= 'ROC Curve')
		 
```


# Classification with Price:
# Categorizing Price:

```{r}
summary(airbnb.1$price)
# We group the patients as per their number of reviews(<=100, 100-160, >160)
L1=sum(as.numeric(airbnb.1$price <=100))
L2=sum(as.numeric(airbnb.1$price<=160))-L1
L3=dim(airbnb.1)[1]-L1 -L2

cat(L1,L2,L3)


price_level<-c(rep ('less_than_100', L1), rep ('between_100_160', L2), rep ('over_160', L3))
airbnb.1=cbind(airbnb.1,price_level)
head(airbnb.1,10)

n=0.30 * dim(airbnb.1)[1]
popsize <- table(airbnb.1$price_level)
popsize
propalloc <- (n*popsize/sum(popsize))
propalloc
unique(airbnb.1$price_level)

```

# Sampling:
```{r}
idx = sampling:::strata(airbnb.1, stratanames=c("price_level"), size=c(1486.2, 882,1157.4), method="srswor")
pricelevel_train =airbnb.1[idx$ID_unit, ]
pricelevel_test = airbnb.1[-idx$ID_unit, ]
```


# Build Model for Price:
```{r}
tree.price <- rpart(factor(price_level)~ room_type +property_type+host_location+host_response_rate+host_is_superhost+host_is_superhost+host_listings_count+
               price+minimum_nights+maximum_nights ,data = pricelevel_train, method = 'class',cp=0.008)
rpart.plot(tree.price)
summary(tree.price)
printcp(tree.price)
plotcp(tree.price)
```


```{r}
tree.price$variable.importance

pred.tree = predict(tree.price, ratinglevel_test, type = "class")
summary(pred.tree)
tb4=table(pred.tree,ratinglevel_test$host_review_level)
tb4
accuracy_Test <- sum(diag(tb4)) / sum(tb4)
print(paste('Accuracy for test', accuracy_Test))

```

```{r}
#Prediction on Price:

p1 <- predict(tree.price, pricelevel_test, type = 'prob')
p1 <- p1[,2]

r <- multiclass.roc(pricelevel_test$price_level, p1, percent = TRUE)
roc <- r[['rocs']]
r1 <- roc[[1]]
plot.roc(r1,
         print.auc=TRUE,
         auc.polygon=TRUE,
         grid=c(0.1, 0.2),
         grid.col=c("green", "red"),
         max.auc.polygon=TRUE,
         auc.polygon.col="lightblue",
         print.thres=TRUE,
         main= 'ROC Curve')
		 
		 
```





















